On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-04-04 docs/mvfits_paper/mvf.tex
adding short statement to further explain physical meaning of negative spin QNMs
Tightening discussion of QNMs as good approx for ringdown

Following the usual treatment, these solutions allow \grad{} from a perturbed Kerr BH at sufficiently late times to be approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with spheroidal harmonics, $_{-2}S\lmn$, of spin weight -2.

@@

>>>>

These solutions allow \grad{} from a perturbed Kerr BH at sufficiently late times to be approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with spheroidal harmonics, $_{-2}S\lmn$, of spin weight -2.

@@

Outside of \bbh{} mergers, these negative spin \qnm{s} generally correspond to perturbations that are counter-rotating relative to the \bh{} spin.
